---
title: "Challenges Module 4"
author: "May Dixon"
date: "September 3000, 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#### CHALLENGE 1:
 
- First, create a vector of 1 word character strings comprising the first line of the Gettysburg address: "Four score and seven years ago our fathers brought forth on this continent, a new nation, conceived in Liberty, and dedicated to the proposition that all men are created equal."

- Then, extract every third element of this vector.

	- Hint 1: Take a look at the {stringr} package and the function `str_split()` to see if you can easily divide a single string into a vector of substrings.

	- Hint 2: If you're ambitious, the following function, `gsub("[[:punct:]]","",*string*)`, applied to `*string*`, will remove punction and special characters from that string.

```{r }

lincoln <- c("Four score and seven years ago our fathers brought forth on this continent, a new nation, conceived in Liberty, and dedicated to the proposition that all men are created equal.")
library (stringr)
lincoln1 <- str_split(lincoln, " ")
class(lincoln1) 
#currently a list with everything in first object
lincoln2<- lincoln1[[1]] # pull out first object to form a vector
lincoln3 <- lincoln2[c(seq(from=3, to=30, by=3))] #pull out over third row

lincoln3

```

As an example for a matrix, suppose you have the following:

``` {r}
m <- matrix(data=1:80,nrow=8,ncol=10,byrow=FALSE)
m
```

You can extract the element in row 4, column 5 and assign it to a new variable, **x**, as follows:

``` {r}
x <- m[4,5]
x
```

You can also extract an entire row or an entire column (or set of rows or set of columns) from a matrix by specifying the desired row or column number(s) and leaving the other value blank.

#### CHALLENGE 2:

- Given the matrix, **m**, above, extract the 2nd, 3rd, and 6th columns and assign them to the variable **x**
```{r}
x<-m[,c(2,3,6)]
x

```
- Given the matrix, **m**, above, extract the 6th to 8th row and assign them to the variable **x**
```{r}
x <- m[c(6,8),]
x
```
- Given the matrix, **m**, above, extract the elements from row 2, column 2 to row 6, column 9 and assign them to the variable **x**
```{r}
x<-m[c(2:6),c(2:9)]
x
```
#### CHALLENGE 3:

- Construct a 4-dimensional, 400 element array (5 x 5 x 4 x 4) named **a** consisting of the numbers 400 to 1 (i.e., a descending series)

```{r}
a <- array(1:400, dim=c(5,5,4,4))
a
```
- Given this matrix, what would the following return?

	- a[1, 1, 1, 2]
	
	      101

	- a[2, 3, 2, ]

            37 137 237 337
      
	- a[1:5, 1:5, 3, 3]
             [,1] [,2] [,3] [,4] [,5]
            [1,]  251  256  261  266  271
            [2,]  252  257  262  267  272
            [3,]  253  258  263  268  273
            [4,]  254  259  264  269  274
            [5,]  255  260  265  270  275
	      


#### CHALLENGE 4:

- Create a **list** representing this (simplified) primate taxonomy. Hint: you can use **lists** as elements in a list.

- Primates
	- Haplorhini
		- Anthropoidea
			- Platyrrhini
				- Cebidae
				- Atelidae
				- Pitheciidae
			- Catarrhini
				- Cercopithecidae
				- Hylobatidae
				- Hominidae
		- Tarsioidea
			- Tarsiidae
	- Strepsirhini
		- Lorisoidea
			- Lorisidae
			- Galagidae
		- Lemuroidea
			- Cheirogaleidae
			- Lepilemuridae
			- Indriidae
			- Lemuridae
			- Daubentoniidae
			
```{r}
                  Platyrrhini<- c("Cebidae","Atelidae","Pitheciidae")
                  Catarrhini <- c("Cercopithecidae", "Hylobatidae", "Hominidae")
       Anthropoidea <- c(Platyrrhini, Catarrhini)
       Tarsioidea <-"Tarsiidae"
      Haplorhini <- c(Anthropoidea, Tarsioidea)

                  Lorisoidea <- c("Lorisidae","Galagidae")
                  Lemuroidea <- c("Cheirogaleidae", "Lepilemuridae", "Indriidae", "Lemuridae", "Daubentoniidae")
      Strepsirhini <- c(Lorisoidea, Lemuroidea)
      
Primates<- c(Haplorhini, Strepsirhini)

Primates

```
